I programmed the ARM11 emulator with the help of Dylan. We split the work into different folders and files that we'd each program.
~\\

I assigned myself the task of completing the machine structure and functions which I completed quickly once we had decided on a clear structure that would best suit what we were trying to emulate.
~\\

We then discussed how we might go about the pipeline, and then the instructions, concluding that I would write the pipeline, the data processing instruction and branch instruction, and that Dylan would write the multiply and single data transfer instructions.
~\\

We soon realised, having discussed as a team what we should do about instruction handling, that we could amalgamate our work on instructions into shared files. Whilst the assemble binary would only be encoding instructions, and the emulate binary would be decoding and executing instructions, we felt that the instructions could be modified most effectively if they were in one place.
~\\

As the project came together, and we found our solutions to be functioning as expected, we moved onto the GPIO emulation of the Raspberry Pi. We decided as a team that since we didn't have much time left, I should implement the emulation of simulating the GPIO inputs and outputs, whilst the other three members of the team should focus on writing the assembly code to run on the Raspberry Pi.
~\\

I felt that my involvement in the project has taught me a few things. Firstly, I think I need to be more aware and use good programming principles such as commenting when I'm implementing bigger projects. I feel this might have helped my team more if I'd done this as I went through. I also feel that the way I actually implemented what was given could have been improved in that should I have taken a top down approach to implementing the project rather than a bottom up approach at times, the project might have come together more quickly and more effectively. I experienced a large number of memory leaks in my work due to the way I'd implemented it and naturally through a limited understanding of the language when starting the project. I have now rewritten a large amount of the project regarding emulate and this has resulted in a vast improvement in memory performance.